Secure Composition of Robust and Optimising Compilers

### 2024-09-05 tech/main.tex
Add typechecks
.

% Fixing: Too many math alphabets used in version normal.
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[utf8,acmsmall,review,screen,dvipsnames]{acmart}

\usepackage[colorinlistoftodos]{todonotes}
\usepackage[inference]{semantic}
\usepackage{fontawesome5}
\usepackage{listofitems}
\usepackage{glossaries}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{marvosym}
\usepackage{listings}
\usepackage{xspace}
\usepackage{xfrac}
\usepackage{tikz}
\usepackage{soul}
\usepackage{bm}

\setul{0.95ex}{0.3ex}

% https://tex.stackexchange.com/questions/648845/sans-serif-uppercase-greek-no-longer-showing-in-acmart
\DeclareMathAlphabet{\mathsf}{OT1}{LibertinusSans-LF}{m}{n}
\SetMathAlphabet{\mathsf}{bold}{OT1}{LibertinusSans-LF}{bx}{n}

\DeclareMathAlphabet{\mathtt}{OT1}{lmtt}{m}{n}
\SetMathAlphabet{\mathtt}{bold}{OT1}{lmtt}{bx}{n}

@@

%% NOTE that a single column version may be required for 
%% submission and peer review. This can be done by changing
%% the \doucmentclass[...]{acmart} in this template to 
%% \documentclass[manuscript,screen]{acmart}
%% 
%% To ensure 100% compatibility, please check the white list of
%% approved LaTeX packages to be used with the Master Article Template at
%% https://www.acm.org/publications/taps/whitelist-of-latex-packages 
%% before creating your document. The white list page provides 
%% information on how to submit additional LaTeX packages for 
%% review and adoption.
%% Fonts used in the template cannot be substituted; margin 
%% adjustments are not allowed.
%%
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\citestyle{acmauthoryear}

\begin{document}

\title{Secure Composition of Robust and Optimising Compilers}
\begin{abstract}
\begin{center}\small\it
	{This paper uses syntax highlighting accessible to both colourblind and black \& white readers.
	% ~\citep{patrignani2020use}.
% 	% Specifically, it makes use of a $\src{blue}$, $\src{sans\text{-}serif}$ font for a $\src{source}$,
% 	% a $\trg{red}$, $\trg{bold}$ font for an $\trg{intermediate}$,
% 	% and a $\obj{green}$, $\obj{teletype}$ font for a $\obj{target}$ language.
	}
\end{center}
\end{abstract}

@@

@@

\section{General Trace Model}\label{ap:def:gtm}

\begin{gather*}
  \begin{aligned}
  \mi{(Security\ Tag)}~\sigma\bnfdef&\ \lock \mid \unlock\hspace{0.5cm}
  \mi{(Control\ Tag)}~\sandboxtag\bnfdef \ctx\mid\comp\hspace{0.5cm}
  \mi{(Event)}~\event\bnfdef\ \emptyevent \mid \lightning \mid \event[_{b}];\sandboxtag;\sigma \\
  \mi{(Pre\text{-}event)}&~\event[_{b}]\bnfdef\ \ev{Alloc\ \loc\ n} \mid \ev{Dealloc\ \loc} \mid \ev{Use\ \loc\ n} \mid \ev{Branch\ n} \mid \ev{Binop\ n} \\
  \end{aligned}
\end{gather*}

Throughout the paper, sequences are indicated with an overbar (i.e., $\trace$), empty sequences with $\hole{\cdot}$, and concatenation of sequences $\trace[_{1}],\trace[_{2}]$ as $\trace[_{1}]\cdot\trace[_{2}]$.
Prepending elements to sequences uses the same notation: $\event\cdot\trace$.

\begin{definition}\label{ap:def:property}
  A property $\pi$ is a set of traces $\trace$.
\end{definition}
\begin{definition}\label{ap:def:propclass}
  A class $\class$ is a set of properties $\pi$.
\end{definition}
\begin{definition}\label{ap:def:lifting:properties}
  The lifting $\lift{\pi}$ of property $\pi$ is its powerset.
\end{definition}

\section{Properties and Monitors}\label{ap:sec:propmon}

In the following, $\traceagree[]{\pi}{\event}{\absevent}$ and the structure of $\abstrace$ are left abstract.
These are monitor-specific definitions, which are defined in \Cref{ap:subsec:tms,ap:subsec:sms,ap:subsec:ms,ap:subsec:scct,ap:subsec:msscct}.

\begin{figure}[!ht]
  \judgbox{\traceagree{\pi}{\trace}{\abstrace}}{,,Specification-level trace $\trace$ agrees with monitor-level trace $\abstrace$ with respect to property $\pi$.''}
  %
  \typerule{traceagree-empty}{}{
    \traceagree{\pi}{\hole{\cdot}}{\hole{\cdot}}
  }{traceagree-empty}
  %
  \typerule{traceagree-ign-L}{
    \traceagree{\pi}{\trace}{\abstrace}
  }{
    \traceagree{\pi}{\emptyevent\cdot\trace}{\abstrace}
  }{traceagree-ign-L}
  %
  \typerule{traceagree-ign-R}{
    \traceagree{\pi}{\trace}{\abstrace}
  }{
    \traceagree{\pi}{\trace}{\absev{\emptyevent}\cdot\abstrace}
  }{traceagree-ign-R}
  %
  \typerule{traceagree-cons}{
    \traceagree[]{\pi}{\event}{\absevent} &
    \traceagree{\pi}{\trace}{\abstrace}
  }{
    \traceagree{\pi}{\event\cdot\trace}{\absevent\cdot\abstrace}
  }{traceagree-cons}
  \caption{Trace-Agreement relation that equates specification-level traces with monitor-level traces.}\label{fig:stuttereq}
\end{figure}

\bul{A specification trace $\trace$ monitor-satisfies property $\pi$} iff there exists a (final) monitor state $\monitor$ and an abstract trace $\abstrace$ such that the \iul{specification trace $\trace$ agrees with abstract trace $\abstrace$} and \oul{the initial monitor can step to the (final) monitor state $\monitor$ with abstract trace $\abstrace$}.

\begin{definition}[Monitor Satisfaction]\label{def:monsat}
  \bul{$\monsafe{\trace}{\pi}$} $\isdef$ $\exists \abstrace\ \monitor$, \iul{$\traceagree{\pi}{\trace}{\abstrace}$} and \oul{$\monitorcheck{\emptyset}{\monitor}{\abstrace}$}.
\end{definition}

\subsection{Temporal Memory Safety}\label{ap:subsec:tms}

\begin{definition}[\glsfirst*{tms}]\label{ap:def:trace:tmsdef}
  \begin{displaymath}
  \tmssafe:=\left\{\trace \left| \begin{array}{rcl}
                              \ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \ev{Use\ \loc\ n;\sandboxtag;\securitytag}&\le_{\trace}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'} \\
                              \text{if }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\text{ in }\trace&\text{then}&\ev{Dealloc\ \loc;\sandboxtag;\securitytag'}\text{ in }\trace \\
                              \text{at most one }\ev{Dealloc\ \loc;\sandboxtag;\securitytag}&\text{in}&\trace \\
                              \text{at most one }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}&\text{in}&\trace \\
                            \end{array}\right.\right\}
  \end{displaymath}
\end{definition}
Hereby, the notation $\event[_{1}]\le_{\trace}\event[_{2}]$ means that if $\event[_{1}]$ is in $\trace$ and if $\event[_{2}]$ is in $\trace$, then $\event[_{1}]$ appears before $\event[_{2}]$.

$$\;$$
\hrule
$$\;$$
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{allocated}:L\times\sandboxtag,\text{freed}:L\times\sandboxtag\right\} \\
    \mi{(Initial\ Abstract\ Store)}~\emptytmsmon:=&\ \left\{\text{allocated}:\emptyset,\text{freed}:\emptyset\right\}\\
    \mi{(Abstract\ Events)}~\tmsevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc\ \sandboxtag \mid \absev{Dealloc\ }\loc\ \sandboxtag \mid \absev{Use\ }\loc\ \sandboxtag \mid \absterm\\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\tmsevent}}{,,Monitor $\tmsmonitor$ does one step to $\tmsmonitor[']$ given event $\tmsevent$.''}$\;$\\
  %
  \typerule{tms-uninteresting}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
  }{ap:tms-uninteresting}
  %
  \typerule{tms-abort}{
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
  }{ap:tms-abort}
  %
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{allocated} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{freed}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{ap:tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{allocated} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{allocated}: \tmsmonitor.\text{allocated}\cup\left\{(\loc;\sandboxtag)\right\},\text{freed}: \tmsmonitor.\text{freed}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{ap:tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{allocated} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{freed} \\
    \tmsmonitor[']=\left\{\text{allocated}: \tmsmonitor.\text{allocated}\setminus\left\{(\loc;\sandboxtag)\right\},\text{freed}: \tmsmonitor.\text{freed}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{ap:tms-dealloc}
\end{center}
\begin{center}
  \judgbox{\monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\tmstrace}}{,,Monitor $\tmsmonitor$ multi-steps to $\tmsmonitor[']$ given trace $\tmstrace$.''}$\;$\\
  %
  \typerule{tms-refl}{
    \tmsmonitor.\text{allocated}=\emptyset
  }{
    \monitorcheck{\tmsmonitor}{\tmsmonitor}{\hole{\cdot}}
  }{ap:tms-refl}
  %
  \typerule{tms-ign-trans}{
    \monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\tmstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{\emptyevent}\cdot\tmstrace}
  }{ap:tms-ign-trans}
  %
  \typerule{tms-trans}{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\tmsevent} &
    \monitorcheck{\tmsmonitor[']}{\tmsmonitor['']}{\tmstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor['']}{\tmsevent\cdot\tmstrace}
  }{ap:tms-trans}
\end{center}
\begin{center}
  \judgbox{\tmstraceagree[]{\event}{\tmsevent}}{,,Abstract event $\tmsevent$ is equivalent to $\event$ with respect to \gls*{tms}.''}$\;$\\
  %
  \typerule{tms-alloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{ap:tms-alloc-authentic}
  %
  \typerule{tms-dealloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
  }{ap:tms-dealloc-authentic}
  %
  \typerule{tms-use-authentic}{
  }{
    \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
  }{ap:tms-use-authentic}
  %
  \typerule{tms-branch-authentic}{
  }{
    \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{ap:tms-branch-authentic}
  %
  \typerule{tms-binop-authentic}{
  }{
    \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
  }{ap:tms-binop-authentic}
  %
  \typerule{tms-empty-authentic}{
  }{
    \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
  }{ap:tms-empty-authentic}
  %
  \typerule{tms-abort-authentic}{
  }{
    \tmstraceagree[]{\lightning}{\absterm}
  }{ap:tms-abort-authentic}
\end{center}

\begin{lemma}[Traces with Monitor Satisfaction are $\tmssafe$]\label{ap:lem:mon:tmssafe}
  If $\montmssafe{\trace}$, then $\trace\in\tmssafe$. %\Coqed
\end{lemma}
\begin{incompleteproof}
\end{incompleteproof}

\subsection{Spatial Memory Safety}\label{ap:subsec:sms}

\begin{definition}[\glsfirst*{sms}]\label{ap:def:trace:smsdef}
  \begin{displaymath}
  \smssafe:=\left\{\trace \left|\begin{array}{rcl}
                                  \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}, \text{ then }m<n
                                \end{array}\right.\right\}
  \end{displaymath}
\end{definition}
$$\;$$
\hrule
$$\;$$
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\smsmonitor:=&\ L\times\sandboxtag\times\mb{N}\mid\emptysmsmon\\
    \mi{(Abstract\ Events)}~\smsevent\bnfdef&\ \absev{\varepsilon} \mid \absev{Alloc\ }\loc\ \sandboxtag\ n \mid \absev{Use\ }\loc\ \sandboxtag\ n \\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\smsevent}}{,,Monitor $\smsmonitor$ does one step to $\smsmonitor[']$ given event $\smsevent$.''}$\;$\\
  %
  \typerule{sms-uninteresting}{
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor}{\absev{\emptyevent}}
  }{ap:sms-uninteresting}
  %
  \typerule{sms-abort}{
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor}{\absterm}
  }{ap:sms-abort}
  %
  \typerule{sms-use}{
    (\loc;\sandboxtag;m)\in\smsmonitor &
    n<m
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor}{\absev{Use\ }\loc\ \sandboxtag\ n}
  }{ap:sms-use}
  %
  \typerule{sms-alloc}{
    (\loc;\sandboxtag;m)\notin\smsmonitor
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor\cup\left\{(\loc;\sandboxtag;n)\right\}}{\absev{Alloc\ }\loc\ \sandboxtag\ n}
  }{ap:sms-alloc}
\end{center}
\begin{center}
  \judgbox{\monitorcheck{\smsmonitor}{\smsmonitor[']}{\smstrace}}{,,Monitor $\smsmonitor$ multi-steps to $\smsmonitor[']$ given trace $\smstrace$.''}$\;$\\
  %
  \typerule{sms-refl}{
  }{
    \monitorcheck{\smsmonitor}{\smsmonitor}{\hole{\cdot}}
  }{ap:sms-refl}
  %
  \typerule{sms-ign-trans}{
    \monitorcheck{\smsmonitor}{\smsmonitor[']}{\smstrace}
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\absev{\emptyevent}\cdot\smstrace}
  }{ap:sms-ign-trans}
  %
  \typerule{sms-trans}{
    \monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\smsevent} &
    \monitorcheck{\smsmonitor[']}{\smsmonitor['']}{\smstrace}
  }{
    \monitorcheck[]{\smsmonitor}{\smsmonitor['']}{\smsevent\cdot\smstrace}
  }{ap:sms-trans}
\end{center}
\begin{center}
  \judgbox{\smstraceagree[]{\event}{\smsevent}}{,,Abstract event $\smsevent$ is equivalent to $\event$ with respect to \gls*{sms}.''}$\;$\\
  %
  \typerule{sms-alloc-authentic}{
  }{
    \smstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc\ n}
  }{ap:sms-alloc-authentic}
  %
  \typerule{sms-dealloc-authentic}{
  }{
    \smstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
  }{ap:sms-dealloc-authentic}
  %
  \typerule{sms-use-authentic}{
  }{
    \smstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc\ n}
  }{ap:sms-use-authentic}
  %
  \typerule{sms-branch-authentic}{
  }{
    \smstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{ap:sms-branch-authentic}
  %
  \typerule{sms-binop-authentic}{
  }{
    \smstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
  }{ap:sms-binop-authentic}
  %
  \typerule{sms-empty-authentic}{
  }{
    \smstraceagree[]{\emptyevent}{\absev{\emptyevent}}
  }{ap:sms-empty-authentic}
  %
  \typerule{sms-abort-authentic}{
  }{
    \smstraceagree[]{\lightning}{\absterm}
  }{ap:sms-abort-authentic}
\end{center}
\begin{lemma}[Traces with Monitor Satisfaction are $\smssafe$]\label{ap:lem:mon:smssafe}
  If $\monsmssafe{\trace}$, then $\trace\in\smssafe$.\Coqed
\end{lemma}
\begin{proof}
  First, generalize \Cref{ap:def:trace:smsdef} as follows:
  \begin{displaymath}
    \gsmssafe:=\left\{\trace \left|\begin{array}{rcl}
                                    \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}\\
                                    \text{or }(\ev{Use\ \loc\ m;\sandboxtag;\securitytag}\text{ in }\trace\text{ and }(\loc,\sandboxtag,n)\in\smsmonitor),\\
                                    \text{ then }m<n
                                  \end{array}\right.\right\}
  \end{displaymath}
  Then, show ,,If $\mongsmssafe{\trace}$, then $\trace\in\gsmssafe$.'' by inducing on the monitor steps.

  Now specialize this generalization to $\smsmonitor=\emptyset$ and the claim follows as a corollary.
\end{proof}

\subsection{Memory Safety}\label{ap:subsec:ms}

\begin{definition}[\glsfirst*{ms}]\label{ap:def:trace:msdef}
  \begin{displaymath}
    \mssafe:=\tmssafe \cap \smssafe
  \end{displaymath}
\end{definition}
$$\;$$
\hrule
$$\;$$
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\msmonitor:=&\ \tmsmonitor\times\smsmonitor\\
    \mi{(Initial\ Abstract\ Store)}~\emptymsmon:=&\ (\emptytmsmon, \emptysmsmon) \\
    \mi{(Abstract\ Events)}~\msevent:=&\ \tmsevent\times\smsevent \mid \absev{\emptyevent}\\
  \end{aligned}
\end{gather*}
\begin{center}
  \judgbox{\monitorcheck[]{\msmonitor}{\msmonitor[']}{\msevent}}{,,Monitor $\msmonitor$ does one step to $\msmonitor[']$ given event $\msevent$.''}$\;$\\
  %
  \typerule{ms-step}{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\tmsevent} &
    \monitorcheck[]{\smsmonitor}{\smsmonitor[']}{\smsevent}
  }{
    \monitorcheck[]{(\tmsmonitor,\smsmonitor)}{(\tmsmonitor['],\smsmonitor['])}{(\tmsevent,\smsevent)}
  }{ap:ms-step}
\end{center}
\begin{center}
  \judgbox{\monitorcheck{\msmonitor}{\msmonitor[']}{\mstrace}}{,,Monitor $\msmonitor$ multi-steps to $\msmonitor[']$ given trace $\mstrace$.''}$\;$\\
  %
  \typerule{ms-refl}{
    \monitorcheck{\tmsmonitor}{\tmsmonitor}{\hole{\cdot}} &
    \monitorcheck{\smsmonitor}{\smsmonitor}{\hole{\cdot}}
  }{
    \monitorcheck{(\tmsmonitor,\smsmonitor)}{(\tmsmonitor,\smsmonitor)}{\hole{\cdot}}
  }{ap:ms-refl}
  %
  \typerule{ms-ign-trans}{
    \monitorcheck{\msmonitor}{\msmonitor[']}{\mstrace}
  }{
    \monitorcheck[]{\msmonitor}{\msmonitor[']}{\absev{\emptyevent}\cdot\mstrace}
  }{ap:ms-ign-trans}
  %
  \typerule{ms-trans}{
    \monitorcheck[]{\msmonitor}{\msmonitor[']}{\msevent} &
    \monitorcheck{\msmonitor[']}{\msmonitor['']}{\mstrace}
  }{
    \monitorcheck[]{\msmonitor}{\msmonitor['']}{\msevent\cdot\mstrace}
  }{ap:ms-trans}
\end{center}
\begin{center}
  \judgbox{\mstraceagree[]{\event}{\msevent}}{,,Abstract event $\msevent$ is equivalent to $\event$ with respect to \gls*{ms}.''}$\;$\\
  %
  \typerule{ms-some-authentic}{
    \tmstraceagree[]{\event}{\tmsevent} &
    \smstraceagree[]{\event}{\smsevent}
  }{
    \mstraceagree[]{\event}{(\tmsevent,\smsevent)}
  }{ap:ms-some-authentic}
  %
  \typerule{ms-none-authentic}{
    \tmstraceagree[]{\event}{\absev{\emptyevent}} &
    \smstraceagree[]{\event}{\absev{\emptyevent}}
  }{
    \mstraceagree[]{\event}{\absev{\emptyevent}}
  }{ap:ms-none-authentic}
\end{center}

\begin{lemma}[Traces with Monitor Satisfaction are $\mssafe$]\label{ap:lem:mon:mssafe}
  If $\monmssafe{\trace}$, then $\trace\in\mssafe$.\Coqed
\end{lemma}
\begin{proof}
  Corollary of \Cref{ap:lem:mon:tmssafe,ap:lem:mon:smssafe}.
\end{proof}

\subsection{Strict Cryptographic Constant Time}\label{ap:subsec:scct}

>>>>

% Fixing: Too many math alphabets used in version normal.
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[a4paper,12pt]{article}
\usepackage[left=1.5cm,top=1.5cm,right=1.5cm,bottom=1.5cm]{geometry}
\usepackage{parskip}

% https://tex.stackexchange.com/questions/648845/sans-serif-uppercase-greek-no-longer-showing-in-acmart
\DeclareMathAlphabet{\mathsf}{OT1}{LibertinusSans-LF}{m}{n}
\SetMathAlphabet{\mathsf}{bold}{OT1}{LibertinusSans-LF}{bx}{n}
\DeclareMathAlphabet{\mathtt}{OT1}{lmtt}{m}{n}
\SetMathAlphabet{\mathtt}{bold}{OT1}{lmtt}{bx}{n}

@@

\title{Secure Composition of Robust and Optimising Compilers}
\begin{document}

@@

\begin{abstract}
% context
To ensure that secure applications do not leak their secrets, they are required to uphold several security properties such as spatial and temporal memory safety, cryptographic constant time, as well as speculative safety.
% need
Existing work shows how to enforce these properties individually, in an architecture-independent way, by using secure compiler passes that each focus on an individual property.
% task
Unfortunately, given two secure compiler passes that each preserve a possibly different security property, it is unclear what kind of security property is preserved by the composition of those secure compiler passes.
%there is no way to tell what kind of security property will the composition of those secure compilers preserve.

% object
This paper is the first to study what security properties are preserved across the composition of different secure compiler passes.
% findings
Starting from a general theory of property composition for security-relevant properties (such as the aforementioned ones), this paper formalises a theory of composition of secure compilers.
Then, it showcases this theory on a secure multi-pass compiler that preserves the aforementioned security-relevant properties.
% conclusion
Crucially, this paper derives the security of the multi-pass compiler from the composition of the security properties preserved by its individual passes, which include security-preserving as well as optimisation passes.
% 
From an engineering perspective, this is the desirable approach to building secure compilers.
\begin{center}\small\it
	{This paper uses syntax highlighting accessible to both colourblind and black \& white readers.}
\end{center}
\end{abstract}

@@

\section{Background}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Satisfaction}
\bul{A whole program $\varWholeProg$ satisfies a property $\varProperty$} iff \iul{$\varWholeProg$ yields a trace $\varTrace$} such that \oul{$\varTrace$ satisfies $\varProperty$}.

\begin{definition}{\definitionlabel[Property Satisfaction]{prop-sat}}
    \bul{$\sat{\varWholeProg}{\varProperty}$}
    $\isdef$
    if \iul{$\forall\varRuntimeTerm\ \varTrace, %
      \progstepto{\varWholeProg}{\varRuntimeTerm}{\varTrace}$
    },
    then \oul{$\varTrace\in\varProperty$}.
\end{definition}

With this, \definitionref{prop-sat} can be extended as follows: for \bul{a component $\varComponent$ to robustly satisfy a property $\varProperty$}, take an \iul{attacker context $\varContext$ and link it with $\varComponent$}, \oul{the resulting whole program must satisfy $\varProperty$}.

\begin{definition}{\definitionlabel[Robust Property Satisfaction]{prop-rsat}}
  \bul{$\rsat{\varComponent}{\varProperty}$} %
  $\isdef$ %
  \iul{$\forall \varContext\ \varWholeProg$, %
    if $\bopLink{\varContext}{\varComponent} = \varWholeProg$}, %
    then \oul{$\sat{\varWholeProg}{\varProperty}$%
  }.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Property Mappings}

\begin{definition}{\definitionlabel[Universal Image]{universal-image}}
  $ 
    \mapUniversal{\sim}{\trgProperty} := 
      \lrbraces{\srcTrace \mid %
        \forall \trgTrace\ldotp \text{if }\xrelTraces{\srcTrace}{\trgTrace}, \text{ then }%
        \trgTrace\in\trgProperty
      }
  $
\end{definition}
\begin{definition}{\definitionlabel[Existential Image]{existential-image}}
  $ 
    \mapExistential{\sim}{\srcProperty} := 
      \lrbraces{\trgTrace \mid %
        \exists \srcTrace\ldotp \xrelTraces{\srcTrace}{\trgTrace} \text{ and }%
        \srcTrace\in\srcProperty
      }
  $
\end{definition}

The lifting of \definitionref{existential-image} and \definitionref{universal-image} to classes of properties is standard, i.e., simply element-wise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Robust Preservation}

\subsubsection{Differing Trace Models}

A \bul{compiler $\ccST$ for languages $\src{S}$ and $\trg{T}$ robustly preserves a $\trg{T}$-level class $\trgClass$}, if for any \rul{property $\trgProperty$ of class $\trgClass$ and programs $\srcComponent$}, where \iul{$\srcComponent$ robustly satisfies $\mapUniversal{\sim}{\trgProperty}$}, \oul{the compilation of $\srcComponent$, we have that $\ccST\lrpars{\srcComponent}$ robustly satisfies $\trgProperty$}.

\begin{definition}{\definitionlabel[Robust Preservation with $\mapUniversal{\sim}{\cdot}$]{rtp-universal}}
  \begin{center}
    \bul{$\rtpUniversal{\ccST}{\trgClass}{\sim}$}
    %, iff 
    $\isdef$
    \rul{$\forall \trgProperty\in\trgClass, \srcComponent\in\src{S},$} %
    if \iul{$\rsat{\srcComponent}{\mapUniversal{\sim}{\trgProperty}}$},
    then \oul{$\rsat{\ccST\lrpars{\srcComponent}}{\trgProperty}$}.
  \end{center}
\end{definition}
A \bul{compiler $\ccST$ for languages $\src{S}$ and $\trg{T}$ robustly preserves a $\src{S}$-level class $\srcClass$}, if for any \rul{property $\srcProperty$ of class $\srcClass$ and programs $\srcComponent$}, where \iul{$\srcComponent$ robustly satisfies $\srcProperty$}, \oul{the compilation of $\srcComponent$, we have that $\ccST\lrpars{\srcComponent}$ robustly satisfies $\mapExistential{\sim}{\srcProperty}$}.

\begin{definition}{\definitionlabel[Robust Preservation with $\mapExistential{\sim}{\cdot}$]{rtp-existential}}
  \begin{center}
    \bul{$\rtpExistential{\ccST}{\srcClass}{\sim}$}
    %, iff 
    $\isdef$
    \rul{$\forall \srcProperty\in\srcClass, \srcComponent\in\src{S},$} %
    if \iul{$\rsat{\srcComponent}{\srcProperty}$},
    then \oul{$\rsat{\ccST\lrpars{\srcComponent}}{\mapExistential{\sim}{\srcProperty}}$}.
  \end{center}
\end{definition}

\subsubsection{Same Trace Models}

\begin{definition}{\definitionlabel[Robust Preservation]{rtp}}
  \begin{center}
    $\rtp{\ccST}{\varClass}$
    %, iff 
    $\isdef$
    $\forall \varProperty\in\varClass, \srcComponent\in\src{S},$ %
    if $\rsat{\srcComponent}{\varProperty}$,
    then $\rsat{\ccST\lrpars{\srcComponent}}{\varProperty}$.
  \end{center}
\end{definition}
